Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-24 paper.tex
Semicolon to comma

The performance and wake characteristics of cross-flow (vertical-axis) turbines
(CFTs) depend on turbine solidity, blade profile (lift/drag, dynamic stall at
reduced frequency of turbine rotation, symmetry, thickness, camber), blade
pitch, number of blades, strut drag, operational parameters, such as tip speed
ratio; and on the Reynolds number \cite{Para2002}. Note that an average blade
chord Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$,
can be expressed in terms of tip speed ratio $\lambda = \omega R/ U_\infty$,
where $U_\infty$ is the free stream velocity, $c$ is the blade chord length,
$\nu$ is the fluid kinematic viscosity, $\omega$ is the rotor's angular
velocity, and $R$ is the rotor radius. The value of $\lambda$ at which a turbine
reaches peak performance in general decreases with turbine solidity $Nc/(\pi D)$
\cite{Templin1974}, which allows for the use of a simpler Reynolds number based
on turbine diameter $Re_D = U_\infty D/\nu$.

>>>>

The performance and wake characteristics of cross-flow (vertical-axis) turbines
(CFTs) depend on turbine solidity, blade profile (lift/drag, dynamic stall at
reduced frequency of turbine rotation, symmetry, thickness, camber), blade
pitch, number of blades, strut drag, operational parameters, such as tip speed
ratio, and on the Reynolds number \cite{Para2002}. Note that an average blade
chord Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$,
can be expressed in terms of tip speed ratio $\lambda = \omega R/ U_\infty$,
where $U_\infty$ is the free stream velocity, $c$ is the blade chord length,
$\nu$ is the fluid kinematic viscosity, $\omega$ is the rotor's angular
velocity, and $R$ is the rotor radius. The value of $\lambda$ at which a turbine
reaches peak performance in general decreases with turbine solidity $Nc/(\pi D)$
\cite{Templin1974}, which allows for the use of a simpler Reynolds number based
on turbine diameter $Re_D = U_\infty D/\nu$.
